### 2019-05-22 doc/chapters/using_bitcoins.tex
added type to transaction

  val txBuilder: Future[BitcoinTxBuilder] = BitcoinTxBuilder(
    destinations = destinations,
    utxos = utxos,
    feeRate = feeRate,
    changeSPK = creditingSPK,
    network = networkParams
  )
\end{lstlisting}
After calling sign on the transaction builder a valid transaction is returned.
\begin{lstlisting}
  val signedTxF: Future[Transaction] = txBuilder
    .flatMap(_.sign)
    .map {
      tx => println(tx.hex) // transaction in hex for the bitcoin network
    }
\end{lstlisting}
There is no need for a transaction input, since a transaction out point is kind of the pointer to a transaction input.

>>>>

  val txBuilder: Future[BitcoinTxBuilder] = BitcoinTxBuilder(
    destinations = destinations,
    utxos = utxos,
    feeRate = feeRate,
    changeSPK = creditingSPK,
    network = networkParams
  )
\end{lstlisting}
After calling sign on the transaction builder a valid transaction is returned.
\begin{lstlisting}
  val signedTxF: Future[Transaction] = txBuilder
    .flatMap(_.sign)
    .map {
      (tx: Transaction) => println(tx.hex) // transaction in hex for the bitcoin network
    }
\end{lstlisting}
There is no need for a transaction input, since a transaction out point is kind of the pointer to a transaction input.
